### 2014-12-11 PH.tex
search of fixed point

\begin{definition}[Stable state or fixed point]
\label{def:FixPoint}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state, $s$ is a stable state for $PH$ if and only if $next(s) = \emptyset $.
\end{definition}

\begin{definition}[Reachability]
\label{def:Reachability}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state OF $PH$, $s$ is a stable state for $PH$ if and only if $next(s) = \emptyset $. (i.r there is no playable action at the state $s$).
\end{definition}

>>>>

\begin{definition}[Stable state or fixed point]
\label{def:FixPoint1}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state, $s$ is a stable state for $PH$ if and only if $next(s) = \emptyset $.
\end{definition}
\begin{definition}[Lemme: Stable state or fixed point]
\label{def:FixPoint2}
Let $PH = (\PHs,\PHl,\PHa)$ be a Process Hitting and
$s \in \PHl$ be a state, $s$ is a stable state for $PH$ there is no playable action at the state $s$: 
\begin{center}
$\forall h \in \PHa$, $frappeur(h) ~ \notin s ~ \vee ~ cible(h) \notin s$)
\end{center}
\end{definition}

\begin{definition}[Reachability question]
\label{def:reachability}

 If $\ctx \in \PHl$ is a state and $A \in \Proc$ a set of processes, we note $\mathcal{P}(\ctx, A)$ pour \emph{la question d'accessibilité}:
 \begin{center}
  $\exists? \delta \in \Sce(\ctx), A \subseteq \PHget(\ctx \play \delta) $ (i.e $\forall a_i \in A, \PHget{(\ctx \play \delta)}{a}=a_i$).
 \end{center}
With $\Sce(\ctx)$ 
is the set of successively playable actions from the state $\ctx$. 
\end{definition}
